Croder: Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
added code snippet chapter

\title{Croder \\ Bringing the Knowledge of the Crowds into the IDE}
\author{Semih Okur \and Mihai Codoban \and Caius Brindescu \and Kyungho Lee \and Shuo Yuan}
\numberofauthors{5}
\author{
  \alignauthor Semih Okur\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{okur2@illinois.edu}
  \alignauthor Mihai Codoban\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{codo@illinois.edu}
  \alignauthor Caius Brindescu\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{brind@illinois.edu}
   \alignauthor Kyungho Lee\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{klee141@illinois.edu}
  \alignauthor Shuo Yuan\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{syuan20@illinois.edu}
}

@@

\section{Introduction}
\section{Why integrate reviews into the IDE}
\section{Related work}
\section{Selecting code snippets}

\section{Crowds for software development}

One of the main challenges was finding the appropriate crowd to conduct the code review. One of the
first options was the Amazon Mechanical Turk. The main problem with this platform is the lack of
qualified workers. Code Reviewing is a very technical process that requires a large amount of knowledge.
We needed to aim for a platform where we were guaranteed to have the right audience.

@@

\section{Stackexchange code review characteristics}
\section{Interface with StackExchange}
\section{Review management in the IDE}

>>>>

\newcommand{\croder}{\textbf{Croder }}
\newcommand{\IDE}{\textbf{IDE }}
\newcommand{\eclipse}{\textbf{Eclipse }}

\title{Croder: Bringing the Knowledge of the Crowds into the IDE}
\author{Semih Okur \and Mihai Codoban \and Caius Brindescu \and Kyungho Lee \and Shuo Yuan}
\numberofauthors{5}
\author{
  \alignauthor Semih Okur\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{okur2@illinois.edu}
  \alignauthor Mihai Codoban\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{codo@illinois.edu}
  \alignauthor Caius Brindescu\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{brind@illinois.edu}
   \alignauthor Kyungho Lee\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{klee141@illinois.edu}
  \alignauthor Shuo Yuan\\
    \affaddr{University of Illinois at Urbana-Champaign}\\
    \affaddr{Urbana, IL}\\
    \email{syuan20@illinois.edu}
}

@@

\section{Introduction}
\section{Why integrate reviews into the IDE}
\section{Related work}

\section{Crowds for software development}
One of the main challenges was finding the appropriate crowd to conduct the code review. One of the
first options was the Amazon Mechanical Turk. The main problem with this platform is the lack of
qualified workers. Code Reviewing is a very technical process that requires a large amount of knowledge.
We needed to aim for a platform where we were guaranteed to have the right audience.

@@

\section{Stackexchange code review characteristics}
\section{Interface with StackExchange}

\section{Selecting code snippets}

 The first step that the programmer must undergo when composing a code review is of course choosing the code snippets that she desires to be reviewed. The programmer must be able to compose several code snippets that together paint an overall picture of the concept they want to portray. For example snippets could range from lines of code, to loops, to whole classes and packages.

 \croder allows the programmer to easily choose snippets from many places in the \IDE. The reasoning behind this is that if a resource contains or points to code, \croder should be able to transform it into a snippet. Figure \ref{fig:snippetSelection} shows  various resources which \croder can convert to code snippets, such as random editor selections, fields, methods and whole classes. As can be seen, resources originate from diverse views.

 In order to track what snippets have been added to the review so far, a view is provided that holds each snippet. Figure \ref{fig:snippetViewer} illustrates this concept.

 With today's \croder the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer. Section \ref{sec:future} describes a technique which offers suggestions on other possible snippets based on the current ones.

\section{Review management in the IDE}
